Accelerated Magnetic Resonance Imaging by Adversarial Neural Network

### 2018-01-19 paper.tex
Extand intro

Recently machine learning techniques based on manifold learning~\cite{usman2014compressive,bhatia2015fast} and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary} were suggested for MRI reconstruction. MRI reconstruction using convolutional neural networks (CNN) which learns the mapping between zero-filled and fully-sampled MR images was introduced in \cite{wang2016accelerating}. In \cite{Oktay2016}, residual network was proposed for MRI super-resolution. Their model is able to receive multiple inputs acquired from different viewing planes for better image reconstruction. In \cite{lee2017deep,hyun2017deep} a multi-scale residual network, also known as U-net~\cite{ronneberger2015u} is used and provides good reconstruction MR images.
Deep convolutional networks have been successfully applied to acceleration of dynamic MRI in \cite{sandinodeep}. All these works address the reconstruction problem in the image domain rather than the k-space domain.

The proposed framework utilizes recent advances in deep learning, while similarly to the CS methods addresses MRI reconstruction directly from the k-space. Specifically, we use generative adversarial networks (GAN) \cite{goodfellow2014generative,radford2015unsupervised,pathak2016context}. 
GANs are based on the inter-play between two networks: a generator and a discriminator. The generator is capable of learning the distribution over a data-base, and sample realizations of this distribution. 
The discriminator is trained to distinguish between `generated' samples and real ones. This powerful combination has been used for MRI acceleration in~\cite{yu2017deep,mardani2017deep}, and also for generating Computed Tomography (CT)-like images from MRIs~\cite{nie2016medical}.
Here, the generator is used for reconstruction of the entire k-space grid from under-sampled data. Its loss is a combination of an adversarial loss, based on the discriminator output and a fidelity loss with respect to the fully sampled MRI. Promising results are obtained for brain MRI reconstruction using only 40\%, 25\% and 16.6\% of the data.

The paper is organized as follows. Section \ref{method_section} presents some theoretical foundation and our method. Section \ref{experiments_section} describes the experimental results. Conclusions and future directions are describes in section \ref{conclusions_section}.

%--------------------- METHOD --------------------%
\section{Method}\label{method_section}

>>>>

{\color{blue}

Recently different data driven, machine learning techniques were used for MRI acceleration. 
Ravishankar and Bresler~\cite{ravishankar2011mr} proposed a patch dictionary learning based method, for exploit the correlation between image patches in a static image in order to reconstruct MRI from highly under-sampled k-space data. In~\cite{caballero2014dictionary}, an iterative algorithm for dictionary learning used for reconstruction of cardiac cine data with Cartesian k-space under sampling.

Manifold learning has been applied to reconstruction of dynamic MRI in many works. In~\cite{bhatia2014hierarchical}, an hierarchical manifold learned from MR image patches, while each path manifold was consistent with the manifold trained on the entire image. In~\cite{usman2014compressive, bhatia2015fast}, a compressive manifold structure, based on Laplacian eigenmaps, is reconstructed directly from the k-space. The first aims to estimate respiratory motion while the second make use of kernel regression for estimate cardiac motion.
}

A deep learning based methods open the gate to learn the reconstruction from a fully-sampled MR images. MRI reconstruction using convolutional neural networks (CNN) which learns the mapping between zero-filled and fully-sampled MR images was introduced in \cite{wang2016accelerating}. In \cite{Oktay2016}, residual CNN was proposed for MRI super-resolution. Their model is able to receive multiple inputs acquired from different viewing planes for better image reconstruction.

Both~\cite{lee2017deep,hyun2017deep} suggests a multi-scale residual network, also known as U-net~\cite{ronneberger2015u} for reconstruction of MR images. In~\cite{lee2017deep}, the CS problem was formulate as a residual regression problem and solved by a deep convolutional neural network that learned the aliasing artifacts. In~\cite{hyun2017deep}, the U-net corrected MR output image, is used for estimate the missing k-space samples. The fully k-space is then recovered by integrating the sampled k-space according to the sampling mask. Also for dynamic MRI reconstruction, a deep CNN has been successfully applied in~\cite{sandinodeep} and provides better results over the time-consuming CS method. All these works address the reconstruction problem in the image domain rather than the k-space domain.

The proposed framework utilizes recent advances in deep learning, while similarly to the CS methods addresses MRI reconstruction directly from the k-space. Specifically, we use generative adversarial networks (GAN) \cite{goodfellow2014generative,radford2015unsupervised,pathak2016context}. 
GANs are based on the inter-play between two networks: a generator and a discriminator. The generator is capable of learning the distribution over a data-base, and sample realizations of this distribution. 
The discriminator is trained to distinguish between `generated' samples and real ones. This powerful combination has been used for MRI acceleration in~\cite{yu2017deep,mardani2017deep}, and also for generating Computed Tomography (CT)-like images from MRIs~\cite{nie2016medical}.
Here, the generator is used for reconstruction of the entire k-space grid from under-sampled data. Its loss is a combination of an adversarial loss, based on the discriminator output and a fidelity loss with respect to the fully sampled MRI.

{\color{red}
We compare the proposed method to reconstruction results obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling. In addition, we optimized two networks: 1. CNN-L2 - a k-space generator (with same architecture as the proposed method) trained with only L2 loss. 2. IM-CNN-L2 - a network which performs on the image-space and optimized to remove the artifacts caused by under-sampling and zero padding
Promising results are obtained for brain MRI reconstruction using only 40\%, 25\% and 16.6\% of the data.

To assess the clinical usability of the reconstructed images we performed extended validation, anatomy and quantitative measurements.

tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate quality of the proposed MRI reconstruction with respect to other methods, including the widely-used Compressed Sensing.

The paper is organized as follows. Section \ref{method_section} presents some theoretical foundation and our method. Section \ref{experiments_section} describes the experimental results. Conclusions and future directions are describes in section \ref{conclusions_section}.
}
%--------------------- METHOD --------------------%
\section{Method}\label{method_section}
